PyPy's Approach to \\ Implementing Dynamic Languages \\ Using a Tracing JIT Compiler

### 2011-02-07 talk/ibm-feb-2011/talk.tex
add some more concrete examples for traces

\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{ulem}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shadows,shapes,calc,backgrounds,fit}

@@

@@

@@

>>>>

\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{ulem}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{alltt}

\newcommand\redsout[1]{{\color{red}\sout{\hbox{\color{black}{#1}}}}}

@@

\begin{frame}[containsverbatim]
  \frametitle{Example: Dispatching in a Tracing JIT}
\begin{verbatim}
x = ADD(a : Integer, b : Integer)
\end{verbatim}
\end{frame}

\begin{frame}[containsverbatim]
  \frametitle{Example: Dispatching in a Tracing JIT}
\begin{verbatim}
guard_class(a, Integer)
guard_class(b, Integer)
u_a = unbox(a)
u_b = unbox(b)
u_x = int_add(a, b)
x = new(Integer, u_x)
\end{verbatim}
\end{frame}

@@

\begin{frame}[containsverbatim]
  \frametitle{Example: Dependencies in a Tracing JIT}
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
u_a = unbox(a)
u_b = unbox(b)
u_x = int_add(u_a, u_b)
x = new(Integer, u_x)

guard_class(x, Integer)
guard_class(c, Integer)
u_x2 = unbox(x)
u_c = unbox(c)
u_r = int_add(u_x2, u_c)
r = new(Integer, u_r)
\end{alltt}
\end{frame}

\begin{frame}[containsverbatim]
  \frametitle{Example: Dependencies in a Tracing JIT}
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
u_a = unbox(a)
u_b = unbox(b)
u_x = int_add(u_a, u_b)
x = new(Integer, u_x)

\redsout{guard_class(x, Integer)}
guard_class(c, Integer)
u_x2 = unbox(x)
u_c = unbox(c)
u_r = int_add(u_x2, u_c)
r = new(Integer, u_r)
\end{alltt}
\end{frame}

@@

\begin{frame}[containsverbatim]
  \frametitle{Example: Boxing in a Tracing JIT}
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
u_a = unbox(a)
u_b = unbox(b)
u_x = int_add(u_a, u_b)
x = new(Integer, u_x)

guard_class(c, Integer)
u_x2 = unbox(x)
u_c = unbox(c)
u_r = int_add(u_x2, u_c)
r = new(Integer, u_r)
\end{alltt}
\end{frame}

\begin{frame}[containsverbatim]
  \frametitle{Example: Boxing in a Tracing JIT}
\begin{alltt}
guard_class(a, Integer)
guard_class(b, Integer)
u_a = unbox(a)
u_b = unbox(b)
u_x = int_add(u_a, u_b)
\redsout{x = new(Integer, u_x)}

guard_class(c, Integer)
\redsout{u_x2 = unbox(x)}
u_c = unbox(c)
u_r = int_add(u_x, u_c)
r = new(Integer, u_r)
\end{alltt}
\end{frame}
